High-Performance Data Analysis on Janus using Apache Spark

### 2013-12-17 paper.tex
removed image float on grep graphics

\documentclass{article}
\usepackage{natbib}

@@

\section{Evaluation}
% janus
    % overview
%%% DIRECTLY COPY-PASTED TEXT %%%
University of the University of Colorado's Top-
31 (June 2010) supercomputer system, Janus
    % specs (ref)
%%% DIRECTLY COPY-PASTED TEXT %%%
The final Janus computational
system consists of 1,368 nodes, each containing two six-
core Intel Xeon Westmere-EP chips at 2.8 GHz, for a total
of 2,736 processors and 16,416 cores with a theoretical
peak performance of 184 TFLOP/s. Each core has 2
GB of 1333 MHz DDR3 RAM for a total of 24 GB per
node and 32 TB of memory in the entire system. (REF)
% spark
    % reason for spark (diskless)
    % installation (default???)
    % version number (Spark 0.8.0, Scala 2.9.3)
% purpose of trials (speedup, efficiency, install on Janus)
    % find ideal configurations

@@

\subsection{Results}
% small grep test
    % serial run time (graph)
    % efficiency (graph)
    % karp flatt (graph)
% cores grep test
    % scale up, workers per node (graph)
% large grep test
    % serial run time (graph)
% pagerank test 1
% pagerank test 2
% ...

\section{Discussion}
% small grep test
    % ideal balance between speedup and efficiency
% cores grep test
    % ideal number of workers per core
    % close enough not to matter
    % don't use 6-12
% large grep test
    % ideal workers per problem size
    % follow up test with delay
    % delay (graph)
    % take away on IO
% pagerank test 1
% pagerank test 2
% ...

>>>>

\documentclass{article}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{float}

@@

\section{Evaluation}
% janus
    % overview
    % describe what spark test where
%%% DIRECTLY COPY-PASTED TEXT %%%
University of the University of Colorado's Top-
31 (June 2010) supercomputer system, Janus
    % specs (ref)
%%% DIRECTLY COPY-PASTED TEXT %%%
The final Janus computational
system consists of 1,368 nodes, each containing two six-
core Intel Xeon Westmere-EP chips at 2.8 GHz, for a total
of 2,736 processors and 16,416 cores with a theoretical
peak performance of 184 TFLOP/s. Each core has 2
GB of 1333 MHz DDR3 RAM for a total of 24 GB per
node and 32 TB of memory in the entire system. (REF)
% spark
    % reason for spark (diskless)
    % installation (default???)
    % version number (Spark 0.8.0, Scala 2.9.3)
% purpose of trials (speedup, efficiency, install on Janus)
    % find ideal configurations

@@

\subsection{Results}
% cores grep test
    % scale up, workers per node (graph)
    \begin{figure}[H]
        \centering
        \includegraphics[width=90mm]{images/workerPerNodeTimes.png}
        \caption{Grep runtimes with different workers per node over 20GB file}
        \label{fig:workNodeTime}
    \end{figure}
    \begin{figure}[H]
        \centering
        \includegraphics[width=90mm]{images/workerPerNodeSpeedup.png}
        \caption{Grep speedup with different workers per node over 20GB file}
    \end{figure}
    \begin{figure}[H]
        \centering
        \includegraphics[width=90mm]{images/workerPerNodeEfficiency.png}
        \caption{Grep efficiency with different workers per node over 20GB file}
        \label{fig:workNodeEff}
    \end{figure}
    \begin{figure}[H]
        \centering
        \includegraphics[width=90mm]{images/workerPerNodeKarpFlatt.png}
        \caption{Grep Karp-Flatt metric with different workers per node over
                20GB file}
        \label{fig:workNodeKF}
    \end{figure}
        % stays relative constant, serial is the issue
% large grep test
    % serial run time (graph)
    \begin{figure}[H]
        \centering
        \includegraphics[width=90mm]{images/bigDataTimes.png}
        \caption{Average grep runtimes over 100GB file}
        \label{fig:bigTime}
        % stays relative constant, serial is the issue
    \end{figure}
% pagerank test 1
% pagerank test 2
% ...

\section{Discussion}
% small grep test
    % ideal balance between speedup and efficiency
% cores grep test
    % ideal number of workers per core
    % close enough not to matter
    % don't use 6-12
% large grep test
    % ideal workers per problem size
    % follow up test with delay
    % take away on IO
% pagerank test 1
% pagerank test 2
% ...
